Reproducible development environments with rix

### 2023-12-22 paper.qmd
GA
added an example of a dev env
added rix:
addel library(rix)
overwrite
I > we

As an alternative to the above approach, I will present the [Nix]{.proglang}
package manager, which available for all major operating system and focuses on
installing and building software in a reproducible manner. To make
[Nix]{.proglang} more accessible to [R]{.proglang} programmers, I developed the
[rix]{.pkg} which I will also present in this article.

## The [Nix]{.proglang} package manager

@@

>>>>

As an alternative to the above approach, I will present the [Nix]{.proglang}
package manager, which available for all major operating system and focuses on
installing and building software in a reproducible manner. To make
[Nix]{.proglang} more accessible to [R]{.proglang} programmers, we developed the
[rix]{.pkg} which we will present in this article.

## The Nix package manager

@@

## Reproducible development environments with Nix

```{r}
library(rix)

rix(r_ver = "4.2.2",
    r_pkgs = c("dplyr", "chronicler"),
    project_path = tempdir(),
    print = TRUE)
```
